---
title: "Demo aft format to use as template"
format:
  aft-pdf:
    keep-tex: true  
  aft-html: default
author:
  - name: John Doe
    affiliations:
      - name: Dummy org
        department: Cool Dep
        address: Somewhere
        city: Magic city
        country: best one
        postal-code: 9999
      - Demo Journal
    orcid: 0000-0000-0000-0000
    email: JD@example.org
    url: https://example.org/
  - name: his friend
    affiliations:
      - Another Affiliation
abstract: |
  Only a demo template
keywords: [template, demo]
bibliography: bibliography.bib  
---

## Introduction {#sec-intro}

::: callout-important
This is a dummy example only for the purpose to use this repo as a template starter for creating new formats.  For this `article-format-template` we call our dummy article `aft`. 
:::

::: callout-tip
If this template is named `template.qmd`, `quarto use template` will allow user to renamed `.qmd` before downloading.
:::

Everything for the extensions is in `_extensions/aft` folder. See Quarto doc for details. 

- In `partials`, you'll find the `.tex` partials that can be used. 

- You can have shortcodes available for the format in `shortcodes.lua`

- You can make filter available with the extension in `filter.lua`

This is example content below of what Quarto can do, including some extensions features

## Math {#sec-math}

We can include nice Math within {{< latex >}} like this equation: 

$$
\log(\mu_i) \quad = \quad x_i^\top \beta,
$$ {#eq-mean}

where the regression coefficients $\beta$ are estimated by maximum likelihood (ML) using the iterative weighted least squares (IWLS) algorithm.

::: callout-tip
`{{< latex >}}` is a shortcode syntax where the shortcode is included in the extensions `_extensions\quarto-journals`
:::


```{r}
#| prompt: true
# Loading some data but this chunk won't be shown.
data("quine", package = "MASS")
```

Some code chunk where we are changing our default `echo` option to `true`

```{r}
#| echo: true
m_pois <- glm(Days ~ (Eth + Sex + Age + Lrn)^2, data = quine, family = poisson)
```

## Summary and discussion {#sec-summary}

:::{.callout}

Here we are using a special feature of our format which is the coloring because [pink is a **nice** color]{color=mypink}

:::

## Acknowledgments {.unnumbered}

:::{.callout}

We could include some aknowledgment

:::

## References {.unnumbered}

:::{#refs}

:::

{{< pagebreak >}}

## More technical details {#sec-techdetails .unnumbered}

:::{.callout}

Let's add an appendix after our bibliography.

:::
