---
title: "Demo aft format to use as template"
format:
    aft-pdf:
        keep-tex: true  
    aft-html: default
author:
  - name: John Doe
    affiliations:
      - name: Dummy org
        department: Cool Dep
        address: Somewhere
        city: Magic city
        country: best one
        postal-code: 9999
      - Demo Journal
    orcid: 0000-0000-0000-0000
    email: JD@example.org
    url: https://example.org/
  - name: his friend
    affiliations:
      - Another Affiliation
abstract: |
  Only a demo template
keywords: [template, demo]
bibliography: bibliography.bib  
---

## Introduction {#sec-intro}

::: callout-important
This is a dummy example only for the purpose to use this repo as a template starter for creating new formats.  For this `article-format-template` we call our dummy article `aft`
:::

Everything for the extensions is in `_extensions/aft` folder. See Quarto doc for details. 

- In `partials`, you'll find the `.tex` partials that can be used. 

- You can have shortcodes available for the format in `shortcodes.lua`

- You can make filter available with the extension in `filter.lua`

This is example content below of what Quarto can do, including some extensions features

## Math {#sec-math}

We can include nice Math within {{< latex >}} like this equation: 

$$
\log(\mu_i) \quad = \quad x_i^\top \beta,
$$ {#eq-mean}

where the regression coefficients $\beta$ are estimated by maximum likelihood (ML) using the iterative weighted least squares (IWLS) algorithm.

::: callout-tip
`{{< latex >}}` is a shortcode syntax where the shortcode is included in the extensions `_extensions\quarto-journals`
:::

## Verbatim code chunk

Let's just show a verbatim code chunk which won't be evaluated

```r
glm(formula, data, subset, na.action, weights, offset,
  family = gaussian, start = NULL, control = glm.control(…),
  model = TRUE, y = TRUE, x = FALSE, …)
```

## Table

| Type           | Distribution | Method   | Description                                                                                                                                                                                  |
|---------|---------|---------|-----------------------------------------------|
| GLM            | Poisson      | ML       | Poisson regression: classical GLM, estimated by maximum likelihood (ML)                                                                                                                      |
|                |              | Quasi    | "Quasi-Poisson regression'': same mean function, estimated by quasi-ML (QML) or equivalently generalized estimating equations (GEE), inference adjustment via estimated dispersion parameter |
|                |              | Adjusted | "Adjusted Poisson regression'': same mean function, estimated by QML/GEE, inference adjustment via sandwich covariances                                                                      |
|                | NB           | ML       | NB regression: extended GLM, estimated by ML including additional shape parameter                                                                                                            |
| Zero-augmented | Poisson      | ML       | Zero-inflated Poisson (ZIP), hurdle Poisson                                                                                                                                                  |
|                | NB           | ML       | Zero-inflated NB (ZINB), hurdle NB                                                                                                                                                           |
: Overview of various count regression models. The table is usually placed at the top of the page (`[t!]`), centered (`centering`), has a caption below the table, column headers and captions are in sentence style, and if possible vertical lines should be avoided. {#tbl-overview}

## Illustrations {#sec-illustrations}

We can include some resources provided with our `.qmd` template like a basic frequency distribution of the response variable displayed in
@fig-quine.

::: {#fig-quine}

![](article-visualization.pdf)

Frequency distribution for number of days absent from school.
:::

```{r}
#| prompt: true
# Loading some data but this chunk won't be shown.
data("quine", package = "MASS")
```

Some code chunk where we are changing our default `echo` option to `true`

```{r}
#| echo: true
m_pois <- glm(Days ~ (Eth + Sex + Age + Lrn)^2, data = quine, family = poisson)
```

## Summary and discussion {#sec-summary}

:::{.callout}

Here we are using a special feature of our format which is the coloring because [pink is a **nice** color]{color=mypink}

:::

## Acknowledgments {.unnumbered}

:::{.callout}

We could include some aknowledgment

:::

## References {.unnumbered}

:::{#refs}

:::

{{< pagebreak >}}

## More technical details {#sec-techdetails .unnumbered}

:::{.callout}

Let's add an appendix after our bibliography.

:::
